Software Ticket Quality

### 2017-11-27 proposal/mprop.tex
Add sections in proposed approach and briefly outline what will be done
Continue work on software waste section in the literature review

@@

\textbf{Waste Identification}\cite{Korkala2014WasteIdentification}:
\begin{itemize}
  \item \textbf{What were the goals?}
    The paper had two main goals: 
    \begin{itemize}
      \item a means to identify communication waste in agile software projects 
        environments;
      \item types of communication waste in agile projects.
    \end{itemize}
  \item \textbf{What was the method?}
    The authors collaborated with a medium-sized American software company
    and conducted a series of observations, informal discussions, documents 
    provided by the organization, as well as semi-structured interviews. Moreover,
    the data collection for waste identification was split into 2 parts:
      \begin{itemize}
        \item \textbf{pre-development}: occured before the actual implementation
          begun (e.g.\ backlog creation);
        \item \textbf{development}: happened throughout the implementation
          process (e.g.\ throughout sprints, retrospectives, sprint reviews,
          communication media).
      \end{itemize}
  \item \textbf{What did they learn?}
    They realized the communication waste can be divided into 5 main categories:
      \begin{itemize}
        \item lack of involvement;
        \item lack of shared understanding;
        \item outdated information;
        \item restricted access to information;
        \item scattered information.
      \end{itemize}
    Also, they learned that their way of identifying these types of waste was
    quite efficient and they even recommend it to companies if they'd like
    to conduct such processes internally.
  \item \textbf{Relevance to our work}: the waste identification process can
    be applied to our work so that we can identify possible causes to poor 
    quality tickets.
\end{itemize}

\textbf{Software Development Waste}\cite{sedano2017software}:
\begin{itemize}
  \item \textbf{What were the goals?}
    The main goal of the paper was to identify main types of waste in software
    development projects.
  \item \textbf{What was the method?}
    They conducted a participant-observation study over a long period of time
    at Pivotal, a consultancy software development company. They also interviewed
    multiple engineers and balanced theoretical sampling with analysis to achieve
    the conclusions.
  \item \textbf{What did they learn?}
    They found out there are nine main types of waste in software projects:
    \begin{itemize}
      \item building the wrong feature or product;
      \item mismanaging backlog;
      \item extraneous cognitive load;
      \item rework;
      \item ineffective communication;
      \item waiting/multitasking;
      \item solutions too complex;
      \item psychological distress.
      \item \textbf{Relevance to our work}: this paper complements the previous 
    one on waste identification\cite{Korkala2014WasteIdentification}.
    \end{itemize}
\end{itemize}

\textbf{Waste in Kanban Projects}\cite{ikonen2010exploring}:
\begin{itemize}
  \item \textbf{What were the goals?}
    The authors are trying to find the main sources of waste in Kanban software
    development projects and categorize/rank them based on severity.
  \item \textbf{What was the method?}
    A controlled case study research was employed in a company called Software
    Factory. They conducted semi-structured interviews with 5 of the team
    members both in the beginning in order to collect data as well as at the end 
    of the whole process to categorize the seven types of waste found. Moreover,
    they also measured the overall success of the project based on Shenar's
    techniques (first-second-third-fourth; project efficiency-imapct on the
    customer-business success-preparing for the future).
  \item \textbf{What did they learn?}
    They reached two main findings:
      \begin{itemize}
        \item they found 7 types of waste throughout the project at various
          development stages:
            \begin{itemize}
              \item partially done work;
              \item extra processes;
              \item extra features;
              \item task switching;
              \item waiting;
              \item motion;
              \item defects.
            \end{itemize}
        \item they reached the conclusion that they couldn't explain the success
          of the project even though waste was found.
      \end{itemize}
  \item \textbf{Relevance to our work}: this work completes the findings 
    from the previous work presented as most of the projects we will work with
    will be Agile, thus Kanban-based in terms of issue management.
\end{itemize}

@@

>>>>

Having talked about data and ticket quality and its characteristics, we have 
another issue that inevitably arises in every software project: software waste. 
There are different researches that try to define what waste in software 
development is as well as its main types. One such paper is the one of 
\citet{sedano2017software}. The authors conducted a participant-observation 
study over a long period of time at Pivotal, a consultancy software development
company. They also interviewed multiple engineering and balanced theoretical 
sampling with analysis to elicit the following main types of waste in software
project:
  \begin{itemize}
    \item building the wrong feature or product;
    \item mismanaging backlog;
    \item extraneous cognitive load;
    \item rework;
    \item ineffective communication;
    \item waiting/multitasking;
    \item solutions too complex;
    \item psychological distress.
    \item \textbf{Relevance to our work}: this paper complements the previous 
      one on waste identification\cite{Korkala2014WasteIdentification}.
  \end{itemize}

Even though \citet{sedano2017software} look at waste generally in software 
development, \citet{ikonen2010exploring} try to specifically investigate waste
in kanban-based projects. They controlled a case study research at a company 
called Software factory using semi-structured interviews. The authors reached
two main conclusions:
  \begin{itemize}
    \item they couldn't explain the success of the project even though waste was 
      found;
    \item they identified 7 main types of waste throughout various development
      stages: partially done work, extra processes, extra features, task 
      switching, waiting, motion and defects.
  \end{itemize}
Apart from building the wrong feature/product, the 2 works differ in what types
of waste they identified.

However, defining waste and its main types is not enough - one needs also
ways to identify such waste. \citet{Korkala2014WasteIdentification} propose a
technique to identify communication waste in agile software projects 
environments. The authors collaborated with a medium-sized American software 
company and conducted a series of observations, informal discussions, documents 
provided by the organization, as well as semi-structured interviews. Moreover,
the data collection for waste identification was split into 2 parts:
  \begin{itemize}
    \item \textbf{pre-development}: occurred before the actual implementation
      begun (e.g.\ backlog creation);
    \item \textbf{development}: happened throughout the implementation
      process (e.g.\ throughout sprints, retrospectives, sprint reviews,
      communication media).
  \end{itemize}
Eventually they reached two main conclusions:
  \begin{itemize}
    \item this proposed approach was efficient and the authors recommend it to
      companies if they'd like to conduct such processes internally;
    \item the research elicits 5 main categories for communication waste: lack
      of involvement, lack of shared understanding, outdated information, 
      restricted access to information, scattered information.
  \end{itemize}

@@

@@

\textbf{Research Questions}:
\begin{itemize}
  \item what makes for a quality software ticket that could help developers
    fix the bug/implement the feature faster?
  \item what can be changed in software ticket structure that could ease writing
    such quality software tickets (e.g. add specific fields to the ticket in
    Jira, add instructions as comments on how reporters should write such a 
    ticket)?
  \end{itemize}

\textbf{Experimental design}: conduct a statistical analysis over popular 
open source projects such as Mozilla or Apache and extract tickets via 
some API (maybe REST based). Then, define what makes for 2 similar tickets
(maybe look at story points assigned by experienced triagers; probably we also
need to use only severe/critical ones as they will probably be fixed first
and there will not be any delay, such as waiting for the main developer to come
back from vacation) and then see how much time it took both to be completed
so that we can infer what differences did those 2 tickets have (and see if, for
example, stack traces influenced the duration of the ticket).

\textbf{Independent Variables}: components of tickets - stack traces, steps
to reproduce, grammar error free description and summary, succinct/detailed 
summary, complex/light discussion in comments

\textbf{Dependent Variable}: duration of the ticket between OPEN status and
CLOSED status.
